---
title: "Predicitng Salaries - Linear regression"
output: html_notebook
---

Supervised Machine Learning

Predicting salaries based on years of work experience using linear regression 

The data set considered for the project has one independent variable namely Years of Experience and another dependent variable Annual Salary

Importing the data set
```{r}
dataset = read.csv("Predicting_Salaries.csv")
str(dataset)
```

Splitting the data set into training and test data set

```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$AnnualSalary, SplitRatio = 3/4)
training_set = subset(dataset, split==TRUE)
testing_set=subset(dataset,split==FALSE)
head(training_set)
head(testing_set)
```
Modelling a supervised machine learning model

Fitting simple liner regression to training and testing sets

```{r}
linearReg = lm(formula = AnnualSalary~YearsOfExperience,data = training_set)
summary(linearReg)
```
Predicting testing set results

```{r}
Y_pred = predict(linearReg,newdata=testing_set)
summary(Y_pred)
```
Visualising the Training set results

```{r}
library(ggplot2)
library(scales)
ggplot() +
  geom_point(aes(x=training_set$YearsOfExperience, y=training_set$AnnualSalary),
             colour = 'red') +
  geom_line (aes( x= training_set$YearsOfExperience, y=predict(linearReg, newdata= training_set)),
             colour = 'navy') +
  ggtitle ('Annual Salaries of Data Scientists vs Experience in Years (Training Set)') +
  xlab ('Years of Experience') +
  ylab ('Annual Salary') +
  scale_x_continuous(limits = c(0, 12)) + 
  scale_y_continuous(limits = c(0, 150000)) 
```
Visualising the Test set results

```{r}
ggplot() +
  geom_point(aes(x=testing_set$YearsOfExperience, y=testing_set$AnnualSalary),
             colour = 'red') +
  geom_line (aes( x= training_set$YearsOfExperience, y=predict(linearReg, newdata= training_set)),
             colour = 'navy') +
  ggtitle ('Annual Salaries of Data Scientists vs Experience in Years (Test Set)') +
  xlab ('Years of Experience') +
  ylab ('Annual Salary')+
  scale_x_continuous(limits = c(0, 12)) + 
  scale_y_continuous(limits = c(0, 150000)) 
```





